Consistent Polyhedral Surrogates via Embedding

### 2019-05-15 neurips-19/poly-embed.tex
comments in sec 6

\subsection{Lov\'asz Hinge}
\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}

>>>>

\subsection{Lov\'asz Hinge}
\jessie{Lovasz hinge paper~\cite{yu2018lovasz}}
\raf{I'm tempted to do the following.  We give the abstain counter-example for $k=2$ (I've been using $k$ for the number of elements in the set constructions, but maybe $n$ is better; we can sync up notation later), and then characterize the $k=2$ case informally, showing that the only thing that works is when $f(\{1,2\}) = f(\{1\}) + f(\{2\})$.  Then we can say ``In fact, in full version of the paper, we show a much tighter result: essentially the only Lov\'asz hinge that is consistent is weighted Hamming loss'' or something to that effect.  This leaves room for us to send a journal version to JMLR (for which we'll need some new results), which seems like a good idea for a paper like this: We seem to have useful tools here, so why not let them marinate a bit in NeurIPS, collect feedback, and then publish a more polished/mature version.}
